\documentclass{article}

\title{Project Timeline for Tickets Tonight App}  % Title

\author{Team members: \\ Matt Agra, Weijian Lin, Runhang Li, \\Zhetian Sun, Zhixuan Lai, Jeffery Ouyang \\ \\ Client: \\Ticketmaster}% Author name

\date{\today} % Date for the report

\begin{document}
	
	\maketitle % Insert the title, author and date
	

	\section{\large Requirements, models, and architecture engineering}
	 \hfill \small\textbf{Week 3, Oct 20th - Oct 26th}
		\begin{itemize}
			\item Discuss with clients to make sure what functional and non-functional requirements. Experience the Ticket Master App to understand better how it works. 
			\item Write a clear requirements documentation, validate requirements.
			\item build up models and architectures for each modules of the project, prepare development environment that can efficiently coordinate all the developers, properly group developers into team to focus different parts of the jobs.
		\end{itemize}
	
	\section{\large Functionalities implementation}
	\hfill \small\textbf{Week 4 - 6, Oct 27th - Nov 2nd}
		\begin{itemize}
			\item Design the APIs for searching available tickets nearby
			\item Implement the function to collect and analyze user's behavior and preference and provide ticket recommendation
			\item Implement the function to provide the ability to let users buy tickets online
			\item Implement the function to alert users when ticket price drops
			\item Support Apple Pay and Passbook in the app to make ticket payment easy
			\item Integrate functionalities, prepare for demo
		\end{itemize}
	
	\section{\large Unit Testing}
	\hfill \small\textbf{Week 7, Nov 3rd - Nov 9th}
		\begin{itemize}
			\item For each basic unit of ticket master app, developers should simulate input data for each unit and check if the output matches the expected result.
			\item Check the functionality of each feature for the ticket master. For example, developers need to test whether the location-based recommendation indeed shows nearby ticket suggestion, or if payment through Apple Pay is successful.
		\end{itemize}
	
	\section{\large Integration and System Testing}
	\hfill \small\textbf{Week 8, Nov 10th - Nov 16th}
	\begin{itemize}
		\item Test the integration of front-end UI with the back-end database and logic processing. Test if the data sent from the back-end fulfills user's request and if the time of processing is within the time limit.
		\item Integrate all features into one single app. Test if all features can work together.
		\item Find volunteers to test the app, see if volunteers(customers) can buy a tonight ticket or get nearby recommendation in real-life usage.
	\end{itemize}
	
	\section{\large Operation and Maintenance}
	\hfill \small\textbf{Week 9, Nov 17th - Nov 25th}
	\begin{itemize}
		\item After testing the whole system, developers will release a beat version of the app through Testflight. Developers are expected to collect user's information and feedback to find if there are bugs to be fixed, or any other issues that should be handled.
		\item Examine users' reviews and enhance the performance of existing features or implement more features if users request. 
		\item Iterate the above process to make the app better and better. Make sure some developers will be in charge of maintaining the system.
	\end{itemize}
	
\end{document}