\section{Introduction }
	\subsection{Purpose}
      The purpose of this Software Requirement Specifications (SRS) document is to provide a description about 
      the features and use cases of the Tickets Tonight App 1.0. It will cover all functional and nonfunctional 
      requirements of the product, as well as its UI and technologies being used. This document also details 
      the internal software interfaces and external dependencies and interfaces. This document will describe 
      the whole application system. 
	\subsection{Project Scope}
	  The goal of Tickets Tonight, as its name suggests, is to provide event recommendation, event search and 
	  ticket purchase service which are oriented to last minute decisions. Ticketmaster has been generally 
	  viewed as an endpoint for users to simply purchase the tickets to an event they already have in mind. 
	  Now, with this application, Ticketmaster can extend its services to even the event choosing phase and 
	  event discovery phase of a user’s whole purchasing process. Ticketmaster can better refine and cater to 
	  users who want to buy tickets at the last minute. Ticketmaster has provided sample data through xml 
	  files that contain artist, venue, category, and events data. Ticketmaster has also provided affinity data 
	  which denotes several recommended artists and their scores for a given artist. These data will be used to 
	  generate events available and provide users recommendations. Tickets Tonight will also send 
	  notifications to inform users about events which are still available tonight, based on users’ location, 
	  preference, event date and budget, and lead users to ticket purchase page once they have decided to go.
	\subsection{References}
	\label{reference}
	  Tickets Tonight will use \href{https://parse.com/}{Parse.com} to store the data provided by 
	  Ticketmaster. In order to access the data stored, Ticket Tonight will use Parse\rq s 
	  \href{https://parse.com/docs/ios_guide#top/iOS}{iOS SDK}. To parse the given data from 
	  Ticketmaster, we will be using the python 
	  \href{https://docs.python.org/2/library/xml.etree.elementtree.html}{XML library} and 
	  \href{https://docs.python.org/2/library/json.html}{JSON library}. Ticket Tonight app also uses iOS
	  view controller, including 
	  \href{https://developer.apple.com/library/ios/documentation/WindowsViews/Conceptual/ViewControl
	  	lerCatalog/Chapters/TabBarControllers.html}{TabBarController} and
	  \href{https://developer.apple.com/library/ios/documentation/UserExperience/Conceptual/TableView_
	  	iPhone/CreateConfigureTableView/CreateConfigureTableView.htm}{TableView}. In order to populate the 
	  location map on Apple Maps, we use the \href{https://developer.apple.com/library/mac/documentation/CoreLocation/Reference/CLGeocoder_
	  	class/index.html}{CLGeocoder object} 
	  