\section{Project Experience}
	\subsection{Project Design and Difficulties}
         Our initial design for the project was under the assumption that we would be receiving access to Ticketmaster’s database and API. Under 
         this assumption, we wanted to create a great overall experience that would allow the user to actually be able to purchase the ticket 
         through the app and connect to their Ticketmaster account in order to synchronize the product line. Our original design was using 
         node.js as our server in order to retrieve data from Ticketmaster and have node.js serve as our platform for the data we needed on the 
         app. We also originally wanted to connect the user favorites data to the user account on Ticketmaster’s website so ended up using an 
         anonymous user and store favorites locally. 
         
         One difficulty we had was the designing of the whole application. We really wanted an intuitive way to be able to present the data to the 
         users. Another difficulty we had was combining all the data into a coherent application. Initially we thought about combining all the data 
         to formulate the best recommendation for the user. Another difficulty was converting an actual address to a geopoint in order to mark 
         the location on the map. We needed the geopoint of the location instead of addresses and currently we do this conversion on the mobile 
         device. We could potentially convert all the event locations and save their geopoint instead of the address string.